Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-07 main.tex
Answer 2-1 done (FDR)

\newacronym{degs}{DEGs}{differentially expressed genes}

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
%\Title{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
%\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}

@@

%\subsubsection{Figure 1:h}
\begin{figure}[hp]
\centering
%\widefigure
\includegraphics[width=14cm]{Figure_1_manuscript_workflow} % .PDF is better than .png
%, height=8cm
%\caption % , step 1 (\textcolor{blue}{blue line}: main procedure) and step 2 (\textcolor{orange}{orange line}: analysis export).
%Step 3 (purple line: dealing with surgical margin).
\bcaption{A workflow of \acrshort{hnscc} biomarker discovery}
{The workflow includes data retrieval from TCGA GDC data portal, data process with merging and cleaning,% should be modified aggressively according to different sources of database)
then performing the survival analyses (within \textcolor{yellow}{yellow} square). The Cutoff engine (in R script: cutofFinder\_func.HNSCC.R, a serial cut for grouping patients with \textcolor{asparagus}{low} or \textcolor{red}{high} expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details) might calculate all possible Kaplan-Meier \textit{P} value to find the optimal cutoff value of gene expression for subsequent Cox modeling. The candidate selection performs dissecting and selection of candidate genes by Bonferroni adjusted \textit{P} value as well as a hazard ratio of Cox model, based on the results from the survival analyses. The selected genes will be validated by a independent HNSCC cohort (GSE2837).
(HNSCC: head and neck squamous cell carcinoma; TCGA: the Cancer Genome Atlas; RNA-Seq: RNA sequencing; GDC: Genomic Data Commons.)}
\label{fig:figure1}
\end{figure}

@@

\caption{ The top 10 genes overexpressed with poor prognosis in \acrshort{hnscc} (ranked by Bonferroni adjusted \textit{P} value) }

@@

\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\ 

@@

\caption{The other top 10 genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by Bonferroni corrected \textit{P} value) }

@@

\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\ * Cox's model: \textit{P} value \textless{} 0.001\\lncRNA: Long non-coding RNA\\Remark: \checkmark Validated by GSE2837 ~\end{tabular}}                                                                                                                                                                                                                 \\

@@

Results were considered statistically significant when a two-sided \textit{P} $<$ 0.05, or a lower threshold if indicated.
The \acrfull{fdr} ($< 0.05$) could be used to pick up the optimal \textit{P} value to ensure the control for type I error of the Kaplan-Meier survival test during the cutoff finding procedure.
%statistical inference problems in biomedical and genomic data analysis routinely involve the simultaneous test of thousands, or even millions, of null hypotheses. Examples
There were also multiple correlated tests of null hypotheses in the Kaplan-Meier family during our global scanning of protein-coding genes. The stringent Bonferroni correction could result in an adjusted \textit{P} value to ensure the control for type I error. 
%There were multiple correlated tests in the family of Kaplan-Meier survival hypotheses during our global scanning of protein-coding genes. The stringent Bonferroni correction could result in an adjusted P-value to ensure the control for type I error.

@@

\subsection{Biomarker Selection and Validation}

Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
Bonferroni adjusted (Kaplan-Meier) \textit{P} value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, candidate selection).

Since high correlation between RNA-Seq and microarray results using TCGA data\cite{Guo2013}\cite{Chen2017c},
we analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a}.
%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
The GSE2837 carries out % VUMC, VAMC, UTMDACC (1992-2005)
microarray gene expression (by Affymetrix X3P chips U133\_X3P).
%and relapse-free survival (RFS) data, instead of overall survival in TCGA dataset.

>>>>

\newacronym{ncbi}{NCBI}{National Center for Biotechnology Information}
\newacronym{degs}{DEGs}{differentially expressed genes}

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
%\Title{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma}
%\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}

@@

%\subsubsection{Figure 1:h}
\begin{figure}[hp]
\centering
%\widefigure
\includegraphics[width=14cm]{Figure_1_manuscript_workflow} % .PDF is better than .png
%, height=8cm
%\caption % , step 1 (\textcolor{blue}{blue line}: main procedure) and step 2 (\textcolor{orange}{orange line}: analysis export).
%Step 3 (purple line: dealing with surgical margin).
\bcaption{A workflow of \acrshort{hnscc} biomarker discovery}
{The workflow includes data retrieval from TCGA GDC data portal, data process with merging and cleaning,% should be modified aggressively according to different sources of database)
then performing the survival analyses (within \textcolor{yellow}{yellow} square). The Cutoff engine (in R script: cutofFinder\_func.HNSCC.R, a serial cut for grouping patients with \textcolor{asparagus}{low} or \textcolor{red}{high} expression of a specific gene, to yield a collection of \textit{P} values; please see Materials and Methods section for details) might calculate all possible Kaplan-Meier \textit{P} value (corrected by \acrlong{fdr}, FDR, method) to find the optimal cutoff value of gene expression for subsequent Cox modeling. The candidate selection performs dissecting and selection of candidate genes by Bonferroni adjusted \textit{P} value as well as a hazard ratio of Cox model, based on the results from the survival analyses. The selected genes will be validated by a independent HNSCC cohort (GSE2837).
(HNSCC: head and neck squamous cell carcinoma; TCGA: the Cancer Genome Atlas; RNA-Seq: RNA sequencing; GDC: Genomic Data Commons.)}
\label{fig:figure1}
\end{figure}

@@

\caption{ The top 10 genes overexpressed with poor prognosis in \acrshort{hnscc} (ranked by adjusted \textit{P} value) }

@@

\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier \acrshort{fdr}-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\ 

@@

\caption{The other top 10 genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by corrected \textit{P} value) }

@@

\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier \acrshort{fdr}-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\ * Cox's model: \textit{P} value \textless{} 0.001\\lncRNA: Long non-coding RNA\\Remark: \checkmark Validated by GSE2837 ~\end{tabular}}                                                                                                                                                                                                                 \\

@@

Results were considered statistically significant when a two-sided \textit{P} $<$ 0.05, or a lower threshold if indicated.
The \acrfull{fdr} ($< 0.05$) could be used to pick up the optimal \textit{P} value to ensure the control for type I error of the Kaplan-Meier survival test during the cutoff finding procedure.
%statistical inference problems in biomedical and genomic data analysis routinely involve the simultaneous test of thousands, or even millions, of null hypotheses. Examples
There were also multiple correlated tests of null hypotheses 
%in the Kaplan-Meier family 
during our global scanning of 205,00 protein-coding genes. The stringent Bonferroni correction could result in an adjusted \textit{P} value to ensure the control for type I error. 
%There were multiple correlated tests in the family of Kaplan-Meier survival hypotheses during our global scanning of protein-coding genes. The stringent Bonferroni correction could result in an adjusted P-value to ensure the control for type I error.

@@

\subsection{Biomarker Selection and Validation}
% Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction 才對
Those genes with prognostic impact, whose hazard ratio $>=1.5$ or $<=0.5$ in both Cox's univariate/multivariate model, were assigned as provisional candidates.
Bonferroni adjusted (Kaplan-Meier) \textit{P} value was used to make a ranking of candidates for the final decision (see Figure \ref{fig:figure1}, candidate selection).

Since high correlation between RNA-Seq and microarray results using TCGA data\cite{Guo2013}\cite{Chen2017c},
we analysed GSE2837 dataset (\acrfull{ncbi} GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from PrognoScan (availalbe at http://dna00.bio.kyutech.ac.jp/\\PrognoScan/)\cite{Mizuno2009a}.
%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
The GSE2837 carries out % VUMC, VAMC, UTMDACC (1992-2005)
microarray gene expression (by Affymetrix X3P chips U133\_X3P).
%and relapse-free survival (RFS) data, instead of overall survival in TCGA dataset.
